LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-11-12 main.tex
Reduce size of figure illustrating main & auxiliary grids
Add code to generate convergence figure

\usepackage{amsmath}
\usepackage{commath}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[numbered,framed]{mcode}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=.475\textwidth]{graphics/main_aux_grids}
\end{center}
\caption{Illustration of the main grid (filled circles) and the auxiliary grid (empty circles) used in the computation of the derivative of the flow map in \cref{eq:CG} of the Cauchy-Green strain tensor. The variable \lstinline!auxGridRelDelta! specifies the grid spacing of the auxiliary grid relative to the main grid spacing.}
\label{f:main and auxiliary grids}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.475\textwidth]{graphics/double_gyre/lambda_lcs_convergence}\caption{Convergence of closed $\lambda$-lines for increasing main-grid resolution in the double-gyre model. The outermost closed $\lambda$-line (bold green line) is the vortex boundary. (Top) {[}500x250{]}, $\lambda$-values
of closed orbits from interior to exterior, left gyre: $\lambda=(0.97, 0.98, 0.99, 1.00, 1.01)$, right gyre: $\lambda=(1.00, 1.01, 1.02, 1.03, 1.04)$; (Middle) {[}750x375{]}, left: $\lambda=(0.97, 0.98, 0.99, 1.00, 1.01)$, right: $\lambda=(1.00, 1.01, 1.02, 1.03, 1.04, 1.05)$; (Bottom) {[}1000x500{]}, left: $\lambda=(0.97, 0.98, 0.99, 1.00, 1.01)$, right: $\lambda=(1.00, 1.01, 1.02, 1.03, 1.04, 1.05)$.}
\label{f:double gyre lambda LCS convergence}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{commath}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[numbered,framed]{mcode}
\usepackage{microtype}
\usepackage{pgfplots}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

@@

\pgfplotsset{compat=newest}
\pgfplotsset{plot coordinates/math parser=false}
\newlength\figureheight
\newlength\figurewidth

@@

\begin{figure}
\begin{center}
\includegraphics[width=.325\textwidth]{graphics/main_aux_grids}
\end{center}
\caption{Illustration of the main grid (filled circles) and the auxiliary grid (empty circles) used in the computation of the derivative of the flow map in \cref{eq:CG} of the Cauchy-Green strain tensor. The variable \lstinline!auxGridRelDelta! specifies the grid spacing of the auxiliary grid relative to the main grid spacing.}
\label{f:main and auxiliary grids}
\end{figure}

@@

\begin{figure}
\centering
\setlength\figurewidth{.4\textwidth}
\input{graphics/double_gyre/elliptic_lcs_convergence_500.tikz}
\input{graphics/double_gyre/elliptic_lcs_convergence_750.tikz}
\input{graphics/double_gyre/elliptic_lcs_convergence_1000.tikz}
\caption{Convergence of closed $\lambda$-lines for increasing main-grid resolution in the double-gyre. The outermost closed $\lambda$-line (bold green line) is the vortex boundary. Top: $500 \times 250$, middle: $750 \times 375$, bottom: $1000 \times 500$.}
\label{f:double gyre lambda LCS convergence}
\end{figure}
